Evaluating Storage Systems for Scientific Data in the Cloud

### 2014-05-10 paper.tex
tree
bib fix

>>>>

% ===== 
\usetikzlibrary{arrows,shapes,positioning,shadows,trees}

\tikzset{
  basic/.style  = {draw, text width=2cm, drop shadow, font=\sffamily, rectangle},
  root/.style   = {basic, rounded corners=2pt, thin, align=center,
                   fill=green!30},
  level 2/.style = {basic, rounded corners=6pt, thin,align=center, fill=green!60,
                   text width=8em},
  level 3/.style = {basic, thin, align=left, fill=pink!60, text width=6em}
}
\begin{figure*}
\centering
\begin{tikzpicture}[
  level 1/.style={sibling distance=40mm},
  edge from parent/.style={->,draw},
  >=latex]

% root of the the initial tree, level 1
\node[root] {Cloud Resources}
% The first level, as children of the initial tree
  child {node[level 2] (c1) {Computation}}
  child {node[level 2] (c2) {Storage}}
  child {node[level 2] (c3) {Network}};

% The second level, relatively positioned nodes
\begin{scope}[every node/.style={level 3}]
\node [below of = c1, xshift=15pt] (c11) {CPU speeds};
\node [below of = c11] (c12) {CPU count};
\node [below of = c12] (c13) {CPU kind};

\node [below of = c2, xshift=15pt] (c21) {On node};
\node [below of = c21] (c22) {Block Device};
\node [below of = c22] (c23) {Remote Online};
\node [below of = c23] (c24) {Remote Offline};

\node [below of = c3, xshift=15pt] (c31) {Bandwidth};
\node [below of = c31] (c32) {Latencies};
%\node [below of = c32] (c33) {Resizing tips};
%\node [below of = c33] (c34) {Shortening};
%\node [below of = c34] (c35) {Bending};
\end{scope}

% lines from each level 1 node to every one of its "children"
\foreach \value in {1,2,3}
  \draw[->] (c1.195) |- (c1\value.west);

\foreach \value in {1,...,4}
  \draw[->] (c2.195) |- (c2\value.west);

\foreach \value in {1,...,2}
  \draw[->] (c3.195) |- (c3\value.west);
\end{tikzpicture}
\caption{Scope of current research}
\label{fig:scope}
\end{figure*}
% =====
